PEACE: {\underline P}arallel {\underline E}nvironment for {\underline A}ssembly and {\underline C}lustering of Gene {\underline E}xpression

### 2010-04-20 papers/NAR_web_server_2009/paper.tex
Updated the abstract with a few edits to fix spacing and a couple of spots of changes. I was unable to regenerate the PDF as some of the images/graphs were reported to be missing.

\begin{abstract}
  \mc{We present \peace, a stand alone tool for the high-throughput
    {\it ab initio} clustering of transcript fragment sequences
    produced by Next Generation or Sanger Sequencing technologies,
    freely available from
    \href{http://www.peace-tools.org}{www.peace-tools.org}.  Installed
    and managed through a download-able user-friendly GUI, \peace\/ can
    process large data sets of transcript fragments of length 50 bases
    or greater, grouping the fragments by gene associations with a
    sensitivity compatible to leading clustering tools.  Once
    clustered, the user can employ the GUI's analysis functions,
    allowing the easy collection of statistics and single out specific
    clusters for more comprehensive study or assembly.  Using a novel
    minimum spanning tree based clustering method, \peace is the equal of
    other leading tools in the literature.  It produces results of
    quality virtually identical to those of the \wcd\/ tool when
    applied to Sanger sequences, significantly improved results over
    \wcd when applied the products Next Generate Sequencing
    Technology, and significantly improved results over \capthree in
    both cases.  In short, \peace provides an easily accessible user interface
    for interface with a clustering engine that is the match of the
    leading clustering tools in the literature.}

>>>>

\begin{abstract}
  \mc{We present \peace, a stand alone tool for high-throughput {\it
      ab initio} clustering of transcript fragment sequences produced
    by Next Generation or Sanger Sequencing technologies.  It is
    freely available from
    \href{http://www.peace-tools.org}{www.peace-tools.org}.  Installed
    and managed through a download-able user-friendly GUI, \peace\/
    can process large data sets of transcript fragments of length 50
    bases or greater, grouping the fragments by gene associations with
    a sensitivity compatible to leading clustering tools.  Once
    clustered, the user can employ the GUI's analysis functions,
    facilitating easy collection of statistics and single out specific
    clusters for more comprehensive study or assembly.  Using a novel
    minimum spanning tree based clustering method, \peace is the equal
    of other leading tools in the literature.  It produces results of
    quality virtually identical to those of the \wcd\/ tool when
    applied to Sanger sequences, significantly improved results over
    \wcd\/ when applied the products of Next Generation Sequencing
    Technology, and significantly improved results over \capthree\/ in
    both cases.  In short, \peace\/ provides an intuitive graphical
    user interface and a feature-rich, parallel clustering engine that
    collectively are as good, if not better, than the leading
    clustering tools in the literature.}
